\section{Architectural Design Approach}

The Spring Boot framework concerns itself with developing web applications quickly and efficiently. Since Spring Boot reuses Spring Framework's codebase for many of its' operations, therefore it is impossible to talk about it without mentioning Spring Framework. The three viewpoints that will be discussed in this document are functional, deployment, and information. The three perspectives cross-cutting these viewpoints are usability, evolution, and development resource.\\

The primary focus for Spring Boot will particularly be the functional viewpoint. Functional viewpoint is important because Spring Boot is an open-source web application framework and relies, in large part, on the contributions from the software community. Spring Boot must maintain a clear description of its functionality and project direction so that contributors can meaningfully contribute. To be able to contribute to Spring Boot, it requires Spring Framework knowledge because much of its inner-workings relies on as a foundation.\\

The deployment viewpoint is important for contributors, maintainers and developers as they need to understand the deployment process for new releases containing features and bug fixes, and eventually where it ends up as an artifact for consumers to source from. It is especially important from the perspective of security since Spring Boot includes many external dependencies that have their own schedule for addressing security vulnerability concerns. Since Spring Boot has an automated build pipeline to release their Spring Boot framework, it brings forth an implicit benefit of speed from development to release. Users are able to get new releases in a timely manner and with these new releases, come new features, enchancements, and fixes.\\

The information viewpoint is important because Spring Boot is primarily about making configuration easier for Spring-based web applications. Knowledge of how Spring Boot enacts auto-configurations requires understanding of how data flows at runtime to create a Spring-based application.
